### 2017-08-28 paper/incomeShocks-jde-r1.tex
Fix variable labels and change table notes

% Hours worked and crop loss

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{Crop loss and Hours Worked per Week for Women}
\label{tab:hours}
\begin{tabular}{@{} l D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}   @{}}
\toprule
                                                       &\multicolumn{5}{c}{Hours worked by woman} \\ \midrule
Crop loss - 1-7 months                                 &       1.391         &       1.097         &                     &                     &                     \\
\hs (200 TZS or above)                                 &     (2.319)         &     (2.543)         &                     &                     &                     \\
Crop loss - 1-7 months                                 &                     &       0.037         &                     &                     &                     \\
\hs  \X initial assets (10,000 TZS)                    &                     &     (0.103)         &                     &                     &                     \\
\addlinespace 
Log crop loss - 1-7 months                             &                     &                     &       8.013\sym{**} &      10.073\sym{**} &      15.213         \\
                                                       &                     &                     &     (4.041)         &     (4.526)         &    (25.934)         \\
Log crop loss - 1-7 months                             &                     &                     &                     &      -0.132         &                     \\
\hs \X initial assets (10,000 TZS)                     &                     &                     &                     &     (0.113)         &                     \\
Log crop loss - 1-7 months                             &                     &                     &                     &                     &      -0.647         \\
\hs \X log initial assets                              &                     &                     &                     &                     &     (2.371)         \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{982}        &    \mco{982}        &    \mco{982}        &    \mco{982}        &    \mco{982}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
Log crop loss is log per capita crop loss plus 1.
Log of assets are taken off assets per capita in TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Hours worked and crop loss
\input{../tables/appendix_hours.tex}
